---
title: "Homework # 10: ggplot"
author: "HW10"
output: 
  html_document:
    code_folding: "hide"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, fig.align='center')
library(ggplot2)
```

`mpg` is the dataset that comes with ggplot.  You can use `View(mpg)` to get an overview of the dataset. 

1. Using the `mpg` dataset generate a scatter plot of `cty` (city mileage) and `hwy` (highway mileage).
```{r}
ggplot(data = mpg, aes(x=cty,y=hwy)) + geom_point()
```

2. Add a colour scale to the scatterplot based on the `displ` variable (engine displacement in liters).
```{r}
ggplot(data = mpg, aes(x=cty,y=hwy)) + geom_point(aes(color=hwy))

```

3. Using the `mpg` dataset recreate the plot as shown below.


4. Split the `cty` vs hwy plot into a grid of plots separated by `drv`. 
```{r}
ggplot(data = mpg, aes(x=cty,y=hwy)) + geom_point() + facet_grid(rows = vars(drv))
```


5. Generate a boxplot of `cty` comparing `drv` (f=front wheel, r=rear wheel, 4=4 wheel).


6. Generate density plots of `hwy` coloured by `drv`.  


7. Generate a boxplot of `cty` comparing type of transmission (automatic v.s. manual)
